What's in a Name? Linear Temporal Logic Literally Represents Time Lines

### 2023-01-01 paper/main.tex
line width

        \draw[thick] (s) edge[-latex] (a12) (s) edge[-latex] (a7) (a2) edge[-latex] (a3) (a3) edge[-latex] (a4) (a4) edge[-latex] (a5) (a5) edge[-latex] (a6);
        \draw[thick] (a12) edge[-latex] (a11) (a11) edge[-latex] (a10) (a10) edge[-latex] (a9) (a9) edge[-latex] (a8) (a8) edge[-latex] (a1) (a8) edge[-latex] (a2) (a7) edge[-latex] (a1) (a7) edge[-latex] (a2);

        \end{tikzpicture}}
        \includegraphics[scale=0.3]{examples/ex9/ex9-unsimplified.png}
        \caption{Timeline for un-simplified $\omega$-regular expression $((!a) | (aa^*(!a)))((!a) | (aa^*(!a)))^{\omega}$}
        \label{fig:unsimplified}
    \end{figure}
    \begin{figure}[h!]
        \centering
        \resizebox{.8\textwidth}{!}{
        \begin{tikzpicture}
        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a1) {\!\!\!$\lnot a$\!\!\!};
        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a2) [below=0.4cm of a1] {\!\!\!$a$\!\!\!};
  %      \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p3) [left= 1cm of p2] {\!\!\!$\lnot p$\!\!\!};
        \node (m) at ($(a1)!0.5!(a2)$) {};
        \node[shape=rectangle, fill=gray!30!white, style={minimum width=10.9cm, minimum height=3cm}] (g) [right= -1.1cm of m] {};
        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a1) {\!\!\!$\lnot a$\!\!\!};
        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a2) [below=0.4cm of a1] {\!\!\!$a$\!\!\!};
        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a3) [right= 0.75cm of a2] {\!\!\!$a$\!\!\!};
        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a4) [right= 0.75cm of a3] {\!\!\!$\dots$\!\!\!};
        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a5) [right= 0.75cm of a4] {\!\!\!$a$\!\!\!};
        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a6) [right= 0.75cm of a5] {\!\!\!$\lnot a$\!\!\!};
        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (s) [left= 2cm of m] {\!\!\!start\!\!\!};
        \draw[thick] (s) edge[-latex] (a1) (s) edge[-latex] (a2) (a2) edge[-latex] (a3) (a3) edge[-latex] (a4) (a4) edge[-latex] (a5) (a5) edge[-latex] (a6);
        \end{tikzpicture}}
        \includegraphics[scale=0.3]{examples/ex9/ex9.png}
        \caption{Timeline for simplified $\omega$-regular expression $((!a) | (aa^*(!a)))^{\omega}$}
        \label{fig:simplified}
    \end{figure}
\end{example}

>>>>

        \draw[thick, line width=1.25] (s) edge[-latex] (a12) (s) edge[-latex] (a7) (a2) edge[-latex] (a3) (a3) edge[-latex] (a4) (a4) edge[-latex] (a5) (a5) edge[-latex] (a6);
        \draw[thick, line width=1.25] (a12) edge[-latex] (a11) (a11) edge[-latex] (a10) (a10) edge[-latex] (a9) (a9) edge[-latex] (a8) (a8) edge[-latex] (a1) (a8) edge[-latex] (a2) (a7) edge[-latex] (a1) (a7) edge[-latex] (a2);

        \end{tikzpicture}}
        \includegraphics[scale=0.3]{examples/ex9/ex9-unsimplified.png}
        \caption{Timeline for un-simplified $\omega$-regular expression $((!a) | (aa^*(!a)))((!a) | (aa^*(!a)))^{\omega}$}
        \label{fig:unsimplified}
    \end{figure}
    \begin{figure}[h!]
        \centering
        \resizebox{.8\textwidth}{!}{
        \begin{tikzpicture}
        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a1) {\!\!\!$\lnot a$\!\!\!};
        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a2) [below=0.4cm of a1] {\!\!\!$a$\!\!\!};
  %      \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p3) [left= 1cm of p2] {\!\!\!$\lnot p$\!\!\!};
        \node (m) at ($(a1)!0.5!(a2)$) {};
        \node[shape=rectangle, fill=gray!30!white, style={minimum width=10.9cm, minimum height=3cm}] (g) [right= -1.1cm of m] {};
        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a1) {\!\!\!$\lnot a$\!\!\!};
        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a2) [below=0.4cm of a1] {\!\!\!$a$\!\!\!};
        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a3) [right= 0.75cm of a2] {\!\!\!$a$\!\!\!};
        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a4) [right= 0.75cm of a3] {\!\!\!$\dots$\!\!\!};
        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a5) [right= 0.75cm of a4] {\!\!\!$a$\!\!\!};
        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a6) [right= 0.75cm of a5] {\!\!\!$\lnot a$\!\!\!};
        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (s) [left= 2cm of m] {\!\!\!start\!\!\!};
        \draw[thick, line width=1.25] (s) edge[-latex] (a1) (s) edge[-latex] (a2) (a2) edge[-latex] (a3) (a3) edge[-latex] (a4) (a4) edge[-latex] (a5) (a5) edge[-latex] (a6);
        \end{tikzpicture}}
        \includegraphics[scale=0.3]{examples/ex9/ex9.png}
        \caption{Timeline for simplified $\omega$-regular expression $((!a) | (aa^*(!a)))^{\omega}$}
        \label{fig:simplified}
    \end{figure}
\end{example}
